Belajar Curve Fitting

### 2021-10-18 Semester I/Analisis Numerik Lanjut/Curve Fitting/cfit.Rmd
new

```{r}
n = length(x)
sum_xi = sum(x)
sum_xi_yi = sum(x*y)
sum_yi = sum(y)

A = matrix(c(n,sum_xi,sum_xi,sum_xi_yi),nrow = 2,byrow = T)
A
A_inv = solve(A)
A_inv
b = c(sum_yi,sum_xi_yi)

>>>>

```{r}
n = length(x)
sum_xi = sum(x)
sum_xi_xi = sum(x^2)
sum_xi_yi = sum(x*y)
sum_yi = sum(y)

A = matrix(c(n,sum_xi,sum_xi,sum_xi_xi),nrow = 2,byrow = T)
A
A_inv = solve(A)
A_inv
b = c(sum_yi,sum_xi_yi)
